Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}

### 2020-07-07 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020_rev2.tex
revised paper and reply letter
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\renewcommand{\baselinestretch}{0.99}

@@

\begin{abstract}
\textcolor{blue}{In the current scenario, energy demand rises by 1.3\% each year to 2040, and photovoltaic (PV) systems} have emerged as an alternative to the fossil or nuclear fuel energy generation. The use of formal methods for PV systems is a new subject with significant research spanning only five years. Here we develop and evaluate \textcolor{blue}{an} automated synthesis technique to obtain optimal sizing \textcolor{blue}{of PV systems based on Life Cycle Cost (LCC) analysis. The optimal solution is the lowest cost from a list of equipment that meets the electrical demands from a house, plus the replacement costs and the operation \& maintenance costs over a 20-year period. We propose a variant of the counterexample guided inductive synthesis (CEGIS) approach with two phases linking the technical and cost analysis to obtain the optimization}. We advocate that \textcolor{blue}{our technique} has various advantages if compared to off-the-shelf optimization tools available in the market \textcolor{blue}{for PV systems}. Experimental results from seven case studies demonstrate that we can produce an optimal solution within an acceptable run-time; different software verifiers are evaluated to check performance and soundness. We also compare our approach with a commercial tool specialized in PV systems optimization. Both results are validated with commercial design software; furthermore, some real PV systems comparison are used to show our approach effectiveness. 
\keywords{Formal Synthesis \and Software Verification \and Solar Photovoltaic Systems \and Cyber-Physical Systems.}
\end{abstract}

@@

However, the industry demands the \textcolor{blue}{design solution to be the optimum, considering equipment manufacturers and models available on the market and not just minimum or maximum values of current or power for the optimized items. It is necessary to evaluate the electrical compatibility among the equipment as well. This evaluation can only be achieved with specialized PV optimization software. Therefore, the optimal solution is the lowest cost from a list of equipment that meets the electrical demands of a house. It is based on Life Cycle Cost (LCC) analysis~\cite{Alsadi2018}, where the acquisition and replacement cost are considered over a specific period in years.}

Optimization of PV systems is not a recent topic; since the 1990s, different techniques using different criteria to find ultimate combinations for design parameters, based on intuitive, numerical, and analytical methods, were proposed and developed~\cite{Alsadi2018}. \textcolor{blue}{Concerning the use of automated verification or synthesis to electrical systems, we can mention that} in $2015$, an automated simulation-based verification technique was applied to verify the correctness of power system protection settings~\cite{Sengupta2015}. \textcolor{blue}{In $2017$, it was suggested the application of formal methods to verify and control the behavior of devices in a smart grid (e.g.,~\cite{Abate2017})}. In $2018$, a verification methodology was applied to PV panels and its distributed power point tracking~\cite{Driouich2018}. Lastly, in $2019$, an automated verification methodology was proposed to validate \textcolor{blue}{the sizing of} stand-alone solar PV systems~\cite{TrindadeCordeiro19}. \textcolor{blue}{However, \textit{formal methods and its application to synthesize PV systems are not explored in literature, mainly because it requires background and experience in computer science and PV systems, which is not common}}.

Here we developed a variant of the counterexample guided inductive synthesis (CEGIS)~\cite{AbateCAV2018} technique for synthesizing optimal sizing of stand-alone PV systems. If we provide a correctness specification $\sigma$, our method uses that as a starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$, related to power reliability. In particular, on each iteration, we synthesize the sizing of stand-alone PV systems, but that may not achieve the lowest cost. The candidate solution is then verified via software model checking with a lower bound that serves as the minimum cost of reference. If the verification step does not produce a counterexample, then the lower bound is adjusted; otherwise, we have achieved an optimal PV sizing.

Our work makes three significant contributions to advance the state-of-the-art in PV optimal sizing. First, the use of automated software verification in PV systems was uncommon in recent prior studies; we have shown that formal methods can detect various errors in PV systems designed by existing commercial tools~\cite{TrindadeCordeiro19}. The application of software verification to synthesize PV sizing is novel, thereby leading to more accurate results than existing commercial tools. Second, we evaluate our approach using different state-of-the-art software verifiers to obtain the best performance in our verification back-end for synthesizing optimal PV systems. We compare that to HOMER Pro optimization, with the results being validated with accurate commercial design software called PVsyst. Lastly, we discuss the challenges of applying software verification to PV systems and reflect on lessons learned from this experience.

@@

HOMER Pro was able to evaluate six case studies (cases $1$, $2$, $4$, $5$, $6$, and $7$) under $30$ seconds; it was much faster than the proposed automated synthesis tool (cf.~\textit{EG3}). Case study $3$ could not be simulated since HOMER Pro does not have the battery autonomy adjustment feature, i.e., the tool always tries to feed the given load with electricity $365$ days/year. Some HOMER Pro drawbacks were also noted. (1) System equipment does not include an explicit charge controller. HOMER Pro includes a controller automatically to simulate the charge/discharge of batteries and to meet the load requirement. However, without costs or even with electrical characteristics such as maximum current and voltage, which are common during PV sizing. (2) HOMER Pro requires the inclusion of some battery specification to initiate optimization; however, it does not change the electrical specifications during simulation; the results presented are multiples of the original battery type suggested by the user. For example, it was started with an $83.4$ Ah lead-acid battery, and during simulation, HOMER Pro did not try to use other capacities or types. (3) HOMER Pro does not present the optimal solution in terms of connections of PV panel arrays, just the total in terms of power, i.e., it presents neither the models and the power of each PV panel nor the total of panels in series or parallel. \textcolor{blue}{The cost of every equipment item used in HOMER Pro is an US-based cost, without adaptation regardless of where the equipment is installed.}

@@

Those discrepancies are not easy to address without some real systems validation. However, we use the simulation software PVsyst to validate the optimal sizing produced, as shown in Table~\ref{tab2}. Note that PVsyst has a pre-sizing feature, which presents a minimum recommended sizing of PV panels and batteries (only), but without using manufacturers' data or models for it. This feature was used as reference mainly with HOMER Pro, where there exists no equipment brands or models (only power and capacities specification). PVsyst was used with the field-deployed and the formal synthesis sizing solutions, where brands and models were simulated in PVsyst according to the sized system.
%
\begin{table}
\caption{Optimal sizing validation with PVsyst.}
\label{tab2}
\begin{scriptsize}
\begin{tabular}{c|c|c|c|c}
\hline
\hline
CS & \makecell{PVsyst\\(pre-sizing)}& \makecell{Field\\deployed\\validation}& \makecell{Formal synthesis\\sizing\\validation}& \makecell{HOMER Pro\\sizing\\validation}\\
\hline
\hline
CS 1 & \makecell{P= 1,166 W\\B= 381 Ah\\(minimum)} & \makecell{Not correct sizing \\Avail. $<$ 95\%\\(91.06\%)} & \makecell{No error found \\100\% of avail.} & \makecell{No error found\\Panels oversized in 2.16 $\times$\\Batteries oversized in 1.39 $\times$}\\
\hline
CS 2 & \makecell{P= 1,482 W\\B= 478 Ah\\(minimum)} & \makecell{NA\\There exists no real PV system\\available for comparison} & \makecell{NA \\(TO result\\in Table~\ref{tab1})} & \makecell{No error found\\Panels oversized in 2.6 $\times$\\Batteries oversized in 1.74 $\times$}\\
\hline
CS 3 & \makecell{Not possible to \\simulate\\(autonomy $<$ 24h)} & \makecell{NA\\There exists no real PV system\\available for comparison} & \makecell{Only technique that\\produced solution} & \makecell{NA\\(autonomy $<$ 24h)}\\
\hline
CS 4 & \makecell{P= 1,078 W\\B= 354 Ah\\(minimum)} & \makecell{No error found \\95.76\% of avail.} & \makecell{No error found \\97.37\% of avail.} & \makecell{No error found\\Panels oversized in 2.24 $\times$\\Batteries oversized in 1.41 $\times$}\\
\hline
CS 5 & \makecell{P= 823 W\\B= 268 Ah\\(minimum)} & \makecell{No error found \\100\% of avail.} & \makecell{No error found \\100\% of avail.} & \makecell{No error found\\Panels oversized in 1.93 $\times$\\Batteries oversized in 1.56 $\times$}\\
\hline
CS 6 & \makecell{P= 1,299 W\\B= 421 Ah\\(minimum)} & \makecell{Not correct sizing \\Avail. $<$ 95\%\\(85.65\%)} & \makecell{No error found \\100\% of avail.} & \makecell{No error found\\Panels oversized in 2.42 $\times$\\Batteries oversized in 1.38 $\times$}\\
\hline
CS 7 & \makecell{P= 4,263 W\\B= 1,384 Ah\\(minimum)} & \makecell{NA\\There exists no real PV system\\available for comparison} & \makecell{NA \\(UNSAT result\\in Table~\ref{tab1})} & \makecell{No error found\\Panels oversized in 2.9 $\times$\\Batteries oversized in 1.99 $\times$}\\
\hline
\hline
\end{tabular}
\\Legend: CS = case study; NA = sizing not available for validation; B = batteries capacity; P = panels power; Avail.= Availability (expected of 95\% or greater as a design requirement).
\end{scriptsize}
\end{table}

@@

\textcolor{blue}{Related to the cost (LCC) present by both tools, HOMER Pro do not use the real cost for PV systems deployed in Brazil; therefore the optimal solution presented by HOMER Pro is notoriously cheaper than our technique. However, considering that the aim is to present an optimal PV sizing solution that is feasible and closer to the market prices, then our technique is more indicated.}

@@

We have reported a favorable assessment of the proposed method. Nevertheless, we have also identified four threats to the validity of our results that constitute future work. First, improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the study more accurate. Second, improvement of the system cost analysis by adding operational and maintenance costs to the adopted LCC analysis. Third, increase the equipment and manufacturers database: this will increase the optimization complexity, but the result will also allow improved sizing. Lastly, the underlying software verifiers employed here perform bit-precise verification based on the Floating-Point (FP) theory. We could use a real arithmetic strategy to tackle these equations; however, in this study, we have exploited the FP arithmetic, which is an approximation of the real one.

@@

Our novelty relies on a practical approach to pursue the optimal PV systems' optimal solution using contemporary formal methods. The use of formal synthesis to design PV systems has no precedent in literature; we show that our approach results, using seven case studies, are promising. Our synthesis tool can present a solution that is far more detailed and closer to commercial reality than the solution given by the commercial tool. In particular, the battery autonomy feature, together with the details of every component of a PV system solution, is an advantage for our synthesis approach. These technical details are essential for the PV system owner since the industry demands proximity between the result presented by optimization tools and the items of equipment for solar systems available on the market.

Our synthesis technique was developed and used open-source software verifiers and the environment, in contrast to the optimization and simulation tools used in this work. We have also observed that state-of-the-art software verifiers are doing an excellent job of solving hard verification conditions based on the underlying SAT/SMT solvers. Lastly, the use of data from real deployed systems in Brazil and the validation through PVsyst was essential to validate the comparison. \textcolor{blue}{Now that we proved that our technique has a promising result for PV system sizing optimization, our focus for future work will be the improvement with the search mechanism used in the {\sc Verify} phase of our synthesis technique, to speed up the time to respond. Our plan is to use binary search or even a solver that is specific to perform optimization with model checking as $\nu Z$~\cite{BjornerPF15}.}

>>>>

\renewcommand{\baselinestretch}{0.97}

@@

\begin{abstract}
\textcolor{blue}{In the current scenario, energy demand rises by 1.3\% each year to 2040, and photovoltaic (PV) systems} have emerged as an alternative to the fossil or nuclear fuel energy generation. The use of formal methods for PV systems is a new subject with significant research spanning only five years. Here we develop and evaluate \textcolor{blue}{an} automated synthesis technique to obtain optimal sizing \textcolor{blue}{of PV systems based on Life Cycle Cost (LCC) analysis. The optimal solution is the lowest cost from a list of equipment that meets the electrical demands from a house, plus the replacement costs and the operation \& maintenance costs over $20$ years. We propose a variant of the counterexample guided inductive synthesis (CEGIS) approach with two phases linking the technical and cost analysis to obtain the optimization}. We advocate that \textcolor{blue}{our technique} has various advantages if compared to off-the-shelf optimization tools available in the market \textcolor{blue}{for PV systems}. Experimental results from seven case studies demonstrate that we can produce an optimal solution within an acceptable run-time; different software verifiers are evaluated to check performance and soundness. We also compare our approach with a commercial tool specialized in PV systems optimization. Both results are validated with commercial design software; furthermore, some real PV systems comparison are used to show our approach effectiveness. 
\keywords{Formal Synthesis \and Software Verification \and Solar Photovoltaic Systems \and Cyber-Physical Systems.}
\end{abstract}

@@

However, the industry demands the \textcolor{blue}{design solution to be the optimum, considering equipment manufacturers and models available on the market and not just minimum or maximum values of current or power for the optimized items. It is necessary to evaluate the electrical compatibility among the equipment as well. This evaluation can only be achieved with specialized PV optimization software. Therefore, the optimal solution is the lowest cost from a list of equipment that meets the house's electrical demands. It is based on Life Cycle Cost (LCC) analysis~\cite{Alsadi2018}, where the acquisition and replacement cost are considered over a specific period in years.}

Optimization of PV systems is not a recent topic; since the 1990s, different techniques using different criteria to find ultimate combinations for design parameters, based on intuitive, numerical, and analytical methods, were proposed and developed~\cite{Alsadi2018}. \textcolor{blue}{Concerning the use of automated verification or synthesis to electrical systems, we can mention that} in $2015$, an automated simulation-based verification technique was applied to verify the correctness of the power system protection settings~\cite{Sengupta2015}. \textcolor{blue}{In $2017$, Abate suggested the application of formal methods to verify and control the behavior of devices in a smart grid (e.g.,~\cite{Abate2017})}. In $2018$, a verification methodology was applied to PV panels and its distributed power point tracking~\cite{Driouich2018}. Lastly, in $2019$, an automated verification methodology was proposed to validate \textcolor{blue}{the sizing of} stand-alone solar PV systems~\cite{TrindadeCordeiro19}. \textcolor{blue}{However, \textit{formal methods and its application to synthesize PV systems are not explored in literature, mainly because it requires background and experience in computer science and PV systems, which is not common}}.

Here we developed a variant of the counterexample guided inductive synthesis (CEGIS)~\cite{AbateCAV2018} technique for synthesizing optimal sizing of stand-alone PV systems. If we provide a correctness specification $ \sigma $, our method uses that as a starting point and then iteratively produces a sequence of candidate solutions that satisfy $ \sigma $ related to power reliability. In particular, on each iteration, we synthesize the sizing of stand-alone PV systems, but that may not achieve the lowest cost. The candidate solution is then verified via software model checking with a lower bound that serves as the minimum cost of reference. If the verification step does not produce a counterexample, then the lower bound is adjusted; otherwise, we have achieved an optimal PV sizing.

Our work makes three significant contributions to advance the state-of-the-art in PV optimal sizing. First, the use of automated software verification in PV systems was uncommon in recent prior studies; we have shown that formal methods can detect various errors in PV systems designed by existing commercial tools~\cite{TrindadeCordeiro19}. The application of software verification to synthesize PV sizing is novel, thereby leading to more accurate results than existing commercial tools. Second, we evaluate our approach using different state-of-the-art software verifiers to obtain the best performance in our verification backend for synthesizing optimal PV systems. We compare that to HOMER Pro optimization, with the results being validated with accurate commercial design software called PVsyst. Lastly, we discuss the challenges of applying software verification to PV systems and reflect on lessons learned from this experience.

@@

HOMER Pro was able to evaluate six case studies (cases $1$, $2$, $4$, $5$, $6$, and $7$) under $30$ seconds; it was much faster than the proposed automated synthesis tool (cf.~\textit{EG3}). Case study $3$ could not be simulated since HOMER Pro does not have the battery autonomy adjustment feature, i.e., the tool always tries to feed the given load with electricity $365$ days/year. Some HOMER Pro drawbacks were also noted. (1) System equipment does not include an explicit charge controller. HOMER Pro includes a controller automatically to simulate the charge/discharge of batteries and to meet the load requirement. However, without costs or even with electrical characteristics such as maximum current and voltage, which are common during PV sizing. (2) HOMER Pro requires the inclusion of some battery specification to initiate optimization; however, it does not change the electrical specifications during simulation; the results presented are multiples of the original battery type suggested by the user. For example, it was started with an $83.4$ Ah lead-acid battery, and during simulation, HOMER Pro did not try to use other capacities or types. (3) HOMER Pro does not present the optimal solution in terms of connections of PV panel arrays, just the total in terms of power, i.e., it presents neither the models and the power of each PV panel nor the total of panels in series or parallel. \textcolor{blue}{The cost of every equipment item used in HOMER Pro is a US-based cost, without adaptation regardless of where the equipment is installed.}

@@

Those discrepancies are not easy to address without some real systems validation. However, we use the simulation software PVsyst to validate the optimal sizing produced, as shown in Table~\ref{tab2}. Note that PVsyst has a pre-sizing feature, which presents a minimum recommended sizing of PV panels and batteries (only) without using manufacturers' data or models for it. This feature was used as reference mainly with HOMER Pro, where there exists no equipment brands or models (only power and capacities specification). PVsyst was used with the field-deployed and the formal synthesis sizing solutions, where brands and models were simulated in PVsyst according to the sized system.
%
\begin{table}
\caption{Optimal sizing validation with PVsyst.}
\label{tab2}
\begin{scriptsize}
\begin{tabular}{c|c|c|c|c}
\hline
\hline
CS & \makecell{PVsyst\\(pre-sizing)}& \makecell{Field\\deployed\\validation}& \makecell{Formal synthesis\\sizing\\validation}& \makecell{HOMER Pro\\sizing\\validation}\\
\hline
\hline
CS 1 & \makecell{P= 1,166 W\\B= 381 Ah\\(minimum)} & \makecell{Not correct sizing \\Avail. $<$ 95\%\\(91.06\%)} & \makecell{No error found \\100\% of avail.} & \makecell{No error found\\Panels oversized in 2.16 $\times$\\Batteries oversized in 1.39 $\times$}\\
\hline
CS 2 & \makecell{P= 1,482 W\\B= 478 Ah\\(minimum)} & \makecell{NA\\There exists no real PV system\\available for comparison} & \makecell{NA \\(TO result\\in Table~\ref{tab1})} & \makecell{No error found\\Panels oversized in 2.6 $\times$\\Batteries oversized in 1.74 $\times$}\\
\hline
CS 3 & \makecell{Not possible to \\simulate\\(autonomy $<$ 24h)} & \makecell{NA\\There exists no real PV system\\available for comparison} & \makecell{Only technique that\\produced solution} & \makecell{NA\\(autonomy $<$ 24h)}\\
\hline
CS 4 & \makecell{P= 1,078 W\\B= 354 Ah\\(minimum)} & \makecell{No error found \\95.76\% of avail.} & \makecell{No error found \\97.37\% of avail.} & \makecell{No error found\\Panels oversized in 2.24 $\times$\\Batteries oversized in 1.41 $\times$}\\
\hline
CS 5 & \makecell{P= 823 W\\B= 268 Ah\\(minimum)} & \makecell{No error found \\100\% of avail.} & \makecell{No error found \\100\% of avail.} & \makecell{No error found\\Panels oversized in 1.93 $\times$\\Batteries oversized in 1.56 $\times$}\\
\hline
CS 6 & \makecell{P= 1,299 W\\B= 421 Ah\\(minimum)} & \makecell{Not correct sizing \\Avail. $<$ 95\%\\(85.65\%)} & \makecell{No error found \\100\% of avail.} & \makecell{No error found\\Panels oversized in 2.42 $\times$\\Batteries oversized in 1.38 $\times$}\\
\hline
CS 7 & \makecell{P= 4,263 W\\B= 1,384 Ah\\(minimum)} & \makecell{NA\\There exists no real PV system\\available for comparison} & \makecell{NA \\(UNSAT result\\in Table~\ref{tab1})} & \makecell{No error found\\Panels oversized in 2.9 $\times$\\Batteries oversized in 1.99 $\times$}\\
\hline
\hline
\end{tabular}
\\Legend: CS = case study; NA = sizing not available for validation; B = batteries capacity; P = panels power; Avail.= Availability (expected of 95\% or greater as a design requirement).
\end{scriptsize}
\end{table}

@@

\textcolor{blue}{Related to the cost (LCC) present by both tools, HOMER Pro does not use the real cost for PV systems deployed in Brazil; therefore, the optimal solution presented by HOMER Pro is notoriously cheaper than our technique. However, considering that the aim is to present an optimal PV sizing solution that is feasible and closer to the market prices, then our technique is more indicated.}

@@

We have reported a favorable assessment of the proposed method. Nevertheless, we have also identified four threats to the validity of our results that constitute future work. First, improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the study more accurate. Second, improvement of the system cost analysis by adding operational and maintenance costs to the adopted LCC analysis. Third, increase the equipment and manufacturers database: this will increase the optimization complexity, but the result will also allow improved sizing. Lastly, the underlying software verifiers employed here perform bit-precise verification based on the Floating-Point (FP) theory. We could use a real arithmetic strategy to tackle these equations; however, in this study, we have exploited the FP arithmetic, which approximates the real one.

@@

Our novelty relies on a practical approach to pursue the optimal PV systems' optimal solution using contemporary formal methods. The use of formal synthesis to design PV systems has no precedent in literature; we show that our approach results, using seven case studies, are promising. Our synthesis tool can present a solution that is far more detailed and closer to commercial reality than the solution given by the commercial tool. In particular, the battery autonomy feature, together with the details of every component of a PV system solution, is advantageous for our synthesis approach. These technical details are essential for the PV system owner. The industry demands proximity between the result presented by optimization tools and the items of equipment for solar systems available on the market.

Our synthesis technique was developed and used open-source software verifiers and the environment, in contrast to the optimization and simulation tools used in this work. We have also observed that state-of-the-art software verifiers are doing an excellent job of solving hard verification conditions based on the underlying SAT/SMT solvers. Lastly, the use of data from real deployed systems in Brazil and the validation through PVsyst was essential to validate the comparison. \textcolor{blue}{Now that we proved that our technique has a promising result for PV system sizing optimization, our focus for future work will be the improvement with the search mechanism used in the {\sc Verify} phase of our synthesis technique, to speed up the time to respond. We plan to use parallel binary search~\cite{TrindadeDJISC17} or even a solver that is specific to perform optimization with model checking as $\nu Z$~\cite{BjornerPF15}.}
